Manuscript

### 2016-03-06 inst/simulation/manuscript.Rmd
...

```{r initialize}
#library(devtools); install_github("statguy/Winter-Track-Counts")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(WTC)
source("~/git/Winter-Track-Counts/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)

context <- Context$new(resultDataDirectory=wd.data.results, processedDataDirectory=wd.data.processed, rawDataDirectory=wd.data.raw, scratchDirectory=wd.scratch, figuresDirectory=wd.figures)
scenarios <- c("A","B","C","D","E","F")
allScenarios <- c(scenarios, paste0(scenarios, "combined"), paste0(scenarios, "10days"))
modelNames <- c("SmoothModel-nbinomial-matern-ar1", "SmoothModel-nbinomial-ar1", "SmoothModelMean-nbinomial-ar1", "FMPModel", "SmoothModelMean-nbinomial-ar1-priors1")
iterations <- as.integer(c(1,1,1,1,3,1))
#populationSizeOverEstimate <- 1e999

@@

p <- ggplot(habitatData) + geom_raster(aes(x, y, fill=z), alpha=.4) + scale_fill_manual(values=col) +
  geom_path(data=trackData, aes(long, lat, group=group, colour=observation), alpha=1, size=.3) +#, alpha=observation)) +
  scale_colour_manual(values=c("gray55","black")) + # scale_alpha_manual(values=c(.5,1)) + # gray40
  geom_path(data=surveyRoutesData, aes(long, lat, group=group), size=.3, colour="blue", alpha=.5) +
  coord_fixed(ratio=1, xlim=window[1:2], ylim=window[3:4]) +
  facet_wrap(~scenario) + #coord_equal()
  theme_ms() + theme(panel.border=element_rect(fill="transparent")) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)") +
  theme(legend.position="none", panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), panel.grid.major=element_blank(), plot.margin=unit(c(0,0.1,0,0), "lines")) # top, right, bottom, and left  
saveFigure(p, "manuscript-figure-1.png", width=17, height=15, dpi=200) # draft quality
saveFigure(p, "manuscript-figure-1.pdf", width=17, height=15, dpi=300)

@@

study <- getStudy(scenario="A")
limits <- extent(study$studyArea$boundary)
iterations <- as.integer(c(1,4,1,2,5,34))
year <- 2010
yearLayer <- paste0("X", year)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year)
wdensities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, weightHabitats=T)

@@

wdensitiesScaled$x <- wdensitiesScaled$x / 1000 - 3000
wdensitiesScaled$y <- wdensitiesScaled$y / 1000 - 6000
densitiesScaled$x <- densitiesScaled$x / 1000 - 3000
densitiesScaled$y <- densitiesScaled$y / 1000 - 6000
boundaryDF$lat <- boundaryDF$lat / 1000 - 6000
boundaryDF$long <- boundaryDF$long / 1000 - 3000
agents$x <- agents$x / 1000 - 3000
agents$y <- agents$y / 1000 - 6000
limits@xmin <- limits@xmin / 1000 - 3000
limits@ymin <- limits@ymin / 1000 - 6000
limits@xmax <- limits@xmax / 1000 - 3000
limits@ymax <- limits@ymax / 1000 - 6000
surveyRoutes$x <- surveyRoutes$x / 1000 - 3000
surveyRoutes$y <- surveyRoutes$y / 1000 - 6000
gridTemplate@extent@xmin <- round(gridTemplate@extent@xmin / 1000) - 3000
gridTemplate@extent@ymin <- round(gridTemplate@extent@ymin / 1000) - 6000
gridTemplate@extent@xmax <- round(gridTemplate@extent@xmax / 1000) - 3000
gridTemplate@extent@ymax <- round(gridTemplate@extent@ymax / 1000) - 6000

p1 <- ggplot(wdensitiesScaled) +
  geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  stat_contour(data=densitiesScaled, aes_string(x="x", y="y", z=yearLayer, colour=yearLayer), size=0.1) +
  scale_fill_gradientn(colours=terrain.colors(100), na.value="transparent",
                       guide=guide_legend(title=expression(paste("Population density ", (individuals/km^2)))), trans="log10",
                       breaks=trans_breaks("log10", function(x) 10^x),
                       labels=trans_format("log10", math_format(10^.x))
                       ) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="black", size=0.5) +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0.01,0.01), breaks=pretty_breaks(n=3)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_ms() +
  theme(legend.position="bottom", legend.margin=unit(-1, units="line"), legend.title=element_text(size=10), legend.text=element_text(size=10)) + #top, right, bottom, and left margins
  theme(strip.background=element_blank(), panel.background=element_rect(fill="transparent", colour=NA), panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)")
g1 <- arrangeGrob(p1, main=textGrob("a)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g1, "manuscript-figure-2a.png", width=17, height=8.07, dpi=200) # draft quality
saveFigure(g1, "manuscript-figure-2a.pdf", width=17, height=8.07, dpi=300)

xlabels <- seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5/1000)
xlabels[c(2,4,6,7)] <- ""
p2 <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey", size=0.5) +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5/1000), expand=c(0.01,0.01), labels=xlabels) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5/1000), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_ms() +
  theme(panel.grid.major=element_line(colour="grey")) + #top, right, bottom, and left margins
  theme(strip.background=element_blank(), panel.background=element_rect(fill="transparent", colour=NA), panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), legend.position="none", axis.ticks=element_line(colour="grey", size=0.2)) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)")
g2 <- arrangeGrob(p2, main=textGrob("b)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g2, "manuscript-figure-2b.png", width=17, height=7.2, dpi=200) # draft quality
saveFigure(g2, "manuscript-figure-2b.pdf", width=17, height=7.2, dpi=300)

>>>>

```{r initialize}
#library(devtools); install_github("statguy/Winter-Track-Counts")
library(parallel)
library(doMC)
registerDoMC(cores=detectCores())
library(STREM)
source("~/git/STREM/setup/WTC-Boot.R")
library(ggplot2)
library(scales)
library(grid)
library(plyr)
library(gridExtra)

context <- Context$new(resultDataDirectory=wd.data.results, processedDataDirectory=wd.data.processed, rawDataDirectory=wd.data.raw, scratchDirectory=wd.scratch, figuresDirectory=wd.figures, figuresHost=wd.figuresHost)
scenarios <- c("A","B","C","D","E","F")
allScenarios <- c(scenarios, paste0(scenarios, "combined"), paste0(scenarios, "10days"))
modelNames <- c("SmoothModel-nbinomial-matern-ar1", "SmoothModel-nbinomial-ar1", "SmoothModelMean-nbinomial-ar1", "FMPModel", "SmoothModelMean-nbinomial-ar1-priors1")
iterations <- as.integer(c(1,1,1,1,3,1))
#populationSizeOverEstimate <- 1e999

@@

p <- ggplot(habitatData) + geom_raster(aes(x, y, fill=z), alpha=.4) + scale_fill_manual(values=col) +
  geom_path(data=trackData, aes(long, lat, group=group, colour=observation), alpha=1, size=.3) +#, alpha=observation)) +
  scale_colour_manual(values=c("gray55","black")) + # scale_alpha_manual(values=c(.5,1)) + # gray40
  geom_path(data=surveyRoutesData, aes(long, lat, group=group), size=.3, colour="blue", alpha=.5) +
  coord_fixed(ratio=1, xlim=window[1:2], ylim=window[3:4]) +
  facet_wrap(~scenario) + #coord_equal()
  theme_raster() + theme(panel.border=element_rect(fill="transparent")) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)") +
  theme(legend.position="none", panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), panel.grid.major=element_blank(), plot.margin=unit(c(0,0.1,0,0), "lines")) # top, right, bottom, and left  
saveFigure(p, "manuscript-figure-1.png", width=17, height=15, dpi=200) # draft quality
saveFigure(p, "manuscript-figure-1.pdf", width=17, height=15, dpi=300)

@@

study <- getStudy(scenario="A")
year <- 2010
yearLayer <- paste0("X", year)
#iterations <- as.integer(c(1,4,1,4,5,38))
#iterations <- as.integer(c(1,4,1,4,5,16))
iterations <- as.integer(c(1,4,1,4,5,21))
densities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year)
wdensities <- getEstimatedDensity(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, year=year, weightHabitats=T)
surveyRoutes <- getSurveyRouteLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
agents <- getAgentLocations(scenarios=scenarios, modelName=modelNames[1], iterations=iterations, years=year)
limits <- extent(study$studyArea$boundary)

@@

boundaryDF <- ggplot2::fortify(FinlandWTCStudy(context=context, response="canis.lupus")$studyArea$boundary)
wdensitiesScaled$x <- wdensitiesScaled$x / 1000 - 3000
wdensitiesScaled$y <- wdensitiesScaled$y / 1000 - 6000
densitiesScaled$x <- densitiesScaled$x / 1000 - 3000
densitiesScaled$y <- densitiesScaled$y / 1000 - 6000
boundaryDF$lat <- boundaryDF$lat / 1000 - 6000
boundaryDF$long <- boundaryDF$long / 1000 - 3000
agents$x <- agents$x / 1000 - 3000
agents$y <- agents$y / 1000 - 6000
limits@xmin <- limits@xmin / 1000 - 3000
limits@ymin <- limits@ymin / 1000 - 6000
limits@xmax <- limits@xmax / 1000 - 3000
limits@ymax <- limits@ymax / 1000 - 6000
surveyRoutes$x <- surveyRoutes$x / 1000 - 3000
surveyRoutes$y <- surveyRoutes$y / 1000 - 6000
gridTemplate@extent@xmin <- round(gridTemplate@extent@xmin / 1000) - 3000
gridTemplate@extent@ymin <- round(gridTemplate@extent@ymin / 1000) - 6000
gridTemplate@extent@xmax <- round(gridTemplate@extent@xmax / 1000) - 3000
gridTemplate@extent@ymax <- round(gridTemplate@extent@ymax / 1000) - 6000

p1 <- ggplot(wdensitiesScaled) +
  geom_raster(aes_string(x="x", y="y", fill=yearLayer)) +
  stat_contour(data=densitiesScaled, aes_string(x="x", y="y", z=yearLayer, colour=yearLayer), size=0.1) +
  scale_fill_gradientn(colours=c(rep("#00A600FF", 60), terrain.colors(40)), na.value="transparent",
                       guide=guide_legend(title=expression(paste("Population density ", (individuals/km^2)))), trans="log10",
                       breaks=trans_breaks("log10", function(x) 10^x),
                       labels=trans_format("log10", math_format(10^.x))) +
  geom_path(data=boundaryDF, aes(long, lat, group=group), colour="black", size=0.5) +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1.3, colour="white") +
  geom_point(data=agents, aes(x, y, colour=Observed), size=1) + scale_color_manual(values=c("darkgray", "black"), guide=FALSE) +
  scale_x_continuous(limits=c(limits@xmin, limits@xmax), expand=c(0.01,0.01), breaks=pretty_breaks(n=3)) +
  scale_y_continuous(limits=c(limits@ymin, limits@ymax), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_raster() +
  theme(legend.position="bottom", legend.margin=unit(-1, units="line"), legend.title=element_text(size=10), legend.text=element_text(size=10)) + #top, right, bottom, and left margins
  theme(strip.background=element_blank(), panel.background=element_rect(fill="transparent", colour=NA), panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), panel.grid.major=element_blank()) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)")
g1 <- arrangeGrob(p1, main=textGrob("a)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g1, "manuscript-figure-2a.png", width=17, height=8.07, dpi=200) # draft quality
saveFigure(g1, "manuscript-figure-2a.pdf", width=17, height=8.07, dpi=300)

xlabels <- seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5/1000)
xlabels[c(2,4,6,7)] <- ""
p2 <- ggplot(boundaryDF) + geom_path(aes(long, lat, group=group), colour="grey", size=0.5) +
  geom_point(data=surveyRoutes, aes(x, y, colour=intersections), size=1) + scale_color_manual(values=c("darkgrey", "black")) +
  scale_x_continuous(breaks=seq(gridTemplate@extent@xmin, gridTemplate@extent@xmax, 1e5/1000), expand=c(0.01,0.01), labels=xlabels) +
  scale_y_continuous(breaks=seq(gridTemplate@extent@ymin, gridTemplate@extent@ymax, 1e5/1000), expand=c(0.01,0.01)) +
  facet_grid(~scenario) + coord_equal() + theme_raster() +
  theme(panel.grid.major=element_line(colour="grey")) + #top, right, bottom, and left margins
  theme(strip.background=element_blank(), panel.background=element_rect(fill="transparent", colour=NA), panel.margin=unit(0, "lines"), panel.grid.minor=element_blank(), legend.position="none", axis.ticks=element_line(colour="grey", size=0.2)) +
  xlab("X-coordinate (km)") + ylab("Y-coordinate (km)")
g2 <- arrangeGrob(p2, main=textGrob("b)", x=0.01, y=0.01, just="left", gp=gpar(fontsize=10)))
saveFigure(g2, "manuscript-figure-2b.png", width=17, height=7.2, dpi=200) # draft quality
saveFigure(g2, "manuscript-figure-2b.pdf", width=17, height=7.2, dpi=300)
